\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-09-17 parts-tr2global.tex
typo

Process Hitting (PH) and Thomas modelling rely on two different paradigms for the specification of
network dynamics:
Thomas parametrization defines a global function
which associates to each component and each resource configuration a level toward which the component
evolve in the given configuration.
Such a function is always deterministic (whereas the associated asynchronous dynamics can be
indeterministic due to concurrent evolution of components).
In contrast, 
PH models specify a list of local transitions between the levels (processes) of the components (sorts)
that are conditioned with the presence of other processes.
In addition, PH allows the use of intermediate sorts, such as cooperative sorts, that do not refer
to the components of the network.

>>>>

Process Hitting (PH) and Thomas modelling rely on two different paradigms for the specification of
network dynamics:
Thomas parametrization defines a global function
which associates to each component and each resource configuration a level toward which the component
eventually evolves in the given configuration.
Such a function is always deterministic (whereas the associated asynchronous dynamics can be
indeterministic due to concurrent evolution of components).
In contrast, 
PH models specify a list of local transitions between the levels (processes) of the components (sorts)
that are conditioned with the presence of other processes.
In addition, PH allows the use of intermediate sorts, such as cooperative sorts, that do not refer
to the components of the network.
